A Note on Convergence Diagnostics for Multiple Imputation using Chained Equations (MICE)

### 2019-11-24 Simulation/Writeup/NoteConvergence.Rnw
convergence of chain variances added
updated table and figure

Why is $\widehat{R}$ not applicable on MI data? $\widehat{R}$ is not appropriate because it assumes over-dispersed initial values, which means that the initial values of the $m$ imputation chains are 'far away' from the distribution that the chains are converging to. With MI procedures, initial values are chosen such that ... [or maybe even estimated from the observed data??]. This means that at most one initial value is necessary, but probably none at all. [I should look this up.] Without over-dispersed initial states, $\widehat{R}$ can falsely diagnose convergence \citep{broo98}. %would not be sensitive enough to flag non-convergence of MI algorithms: "if over-dispersion does not hold, $\sigma_+^2$ can be too low, which can lead to falsely diagnosing convergence." \cite[p~437]{broo98}. 
This suggests that $\widehat{R}$ would not be sensitive enough to flag non-convergence of MI algorithms. Empirical finding, however, show that the opposite may be true: \cite{lace07} report $\widehat{R}$ values above the threshold of $\widehat{R} < 1.1$ after fifty iterations. %that $\widehat{R}$ will not be smaller than 1.1 before iteration number 50. Therefore, the aim is to replicate empirical finding Lacerda et al. 
Hypothesis of this simulation study is that $\widehat{R}$ will over-estimate non-convergence. [Or use:] Hypothesis based on \cite{lace07} is that the conventional acceptable level of $\widehat{R}$ is too strict for MI data. We expect that the simulation diagnostics will indicate valid inference before $\widehat{R}$ will.

@@

\begin{figure}[h]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{resultsA4.pdf}
  }      
  \caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
    \label{resultssim}
\end{figure}

@@

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Nov 12 17:43:11 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrrr}
  \hline
  &\multicolumn{4}{c}{Simulation Diagnostics}& & \multicolumn{2}{c}{Convergence Diagn.} \\
  \cline{2-5} \cline{7-8}
It. & Bias & Emp. SE & CI width & Cov. rate & & $\widehat{R}$ & Auto-corr. \\ 
  \hline
  1 & -0.135 & 0.115 & 0.637 & 0.930 &  & & \\ 
  2 & -0.088 & 0.125 & 0.691 & 0.990 & & 1.499 & -0.500 \\ 
  3 & -0.090 & 0.112 & 0.623 & 0.950 & &  1.200 & -0.658 \\ 
  4 & -0.093 & 0.116 & 0.645 & 0.980 &  & 1.146 & -0.738 \\ 
  5 & -0.087 & 0.108 & 0.599 & 0.980 &  & 1.098 & -0.711 \\ 
  6 & -0.092 & 0.116 & 0.644 & 0.950 & &  1.090 & -0.674 \\ 
  7 & -0.095 & 0.122 & 0.675 & 1.000 & &  1.063 & -0.588 \\ 
  8 & -0.099 & 0.113 & 0.626 & 0.970 & &  1.058 & -0.523 \\ 
  9 & -0.095 & 0.115 & 0.639 & 1.000 & &  1.044 & -0.519 \\ 
  10 & -0.090 & 0.111 & 0.618 & 0.990 & &  1.048 & -0.414 \\ 
  15 & -0.093 & 0.109 & 0.604 & 0.950 & &  1.020 & -0.339 \\ 
  20 & -0.098 & 0.109 & 0.606 & 0.980 & &  1.023 & -0.234 \\ 
  25 & -0.100 & 0.113 & 0.626 & 0.990 &  & 1.016 & -0.091 \\ 
  30 & -0.091 & 0.118 & 0.654 & 0.960 & &  1.014 & -0.153 \\ 
  40 & -0.088 & 0.117 & 0.650 & 0.990 &  & 1.009 & -0.070 \\ 
  50 & -0.087 & 0.119 & 0.662 & 0.990 &  & 1.009 & -0.029 \\ 
  % 11 & -0.100 & 0.127 & 0.704 & 0.970 & 1.046 & -0.360 \\ 
  % 12 & -0.096 & 0.115 & 0.641 & 0.980 & 1.032 & -0.354 \\ 
  % 13 & -0.098 & 0.120 & 0.664 & 0.960 & 1.034 & -0.328 \\ 
  % 14 & -0.094 & 0.113 & 0.630 & 0.990 & 1.030 & -0.353 \\ 
  % 15 & -0.093 & 0.109 & 0.604 & 0.950 & 1.020 & -0.339 \\ 
  % 16 & -0.094 & 0.114 & 0.630 & 0.980 & 1.025 & -0.272 \\ 
  % 17 & -0.091 & 0.116 & 0.645 & 0.980 & 1.028 & -0.243 \\ 
  % 18 & -0.091 & 0.116 & 0.645 & 0.990 & 1.023 & -0.179 \\ 
  % 19 & -0.087 & 0.114 & 0.630 & 0.980 & 1.024 & -0.281 \\ 
  % 20 & -0.098 & 0.109 & 0.606 & 0.980 & 1.023 & -0.234 \\ 
  % 21 & -0.102 & 0.116 & 0.646 & 0.960 & 1.017 & -0.192 \\ 
  % 22 & -0.095 & 0.114 & 0.633 & 0.980 & 1.016 & -0.119 \\ 
  % 23 & -0.088 & 0.107 & 0.595 & 0.980 & 1.017 & -0.246 \\ 
  % 24 & -0.097 & 0.112 & 0.621 & 0.980 & 1.016 & -0.148 \\ 
  % 25 & -0.100 & 0.113 & 0.626 & 0.990 & 1.016 & -0.091 \\ 
  % 26 & -0.096 & 0.113 & 0.628 & 0.980 & 1.017 & -0.177 \\ 
  % 27 & -0.096 & 0.117 & 0.650 & 0.980 & 1.014 & -0.167 \\ 
  % 28 & -0.102 & 0.116 & 0.645 & 0.960 & 1.015 & -0.038 \\ 
  % 29 & -0.098 & 0.114 & 0.632 & 0.990 & 1.016 & -0.137 \\ 
  % 30 & -0.091 & 0.118 & 0.654 & 0.960 & 1.014 & -0.153 \\ 
  % 31 & -0.098 & 0.115 & 0.639 & 0.980 & 1.012 & -0.101 \\ 
  % 32 & -0.096 & 0.113 & 0.626 & 0.940 & 1.011 & -0.095 \\ 
  % 33 & -0.089 & 0.117 & 0.652 & 0.970 & 1.011 & -0.088 \\ 
  % 34 & -0.093 & 0.115 & 0.639 & 0.960 & 1.013 & -0.061 \\ 
  % 35 & -0.103 & 0.115 & 0.638 & 0.970 & 1.011 & -0.126 \\ 
  % 36 & -0.090 & 0.113 & 0.630 & 0.980 & 1.010 & -0.161 \\ 
  % 37 & -0.098 & 0.122 & 0.675 & 0.990 & 1.011 & -0.070 \\ 
  % 38 & -0.095 & 0.118 & 0.656 & 0.970 & 1.011 & -0.119 \\ 
  % 39 & -0.091 & 0.121 & 0.670 & 0.980 & 1.009 & -0.100 \\ 
  % 40 & -0.088 & 0.117 & 0.650 & 0.990 & 1.009 & -0.070 \\ 
  % 41 & -0.095 & 0.117 & 0.648 & 0.960 & 1.010 & -0.148 \\ 
  % 42 & -0.095 & 0.118 & 0.657 & 0.990 & 1.009 & -0.117 \\ 
  % 43 & -0.095 & 0.116 & 0.645 & 0.980 & 1.009 & -0.055 \\ 
  % 44 & -0.101 & 0.125 & 0.692 & 0.980 & 1.009 & -0.068 \\ 
  % 45 & -0.085 & 0.117 & 0.651 & 0.980 & 1.008 & -0.086 \\ 
  % 46 & -0.092 & 0.117 & 0.649 & 0.970 & 1.008 & -0.048 \\ 
  % 47 & -0.095 & 0.115 & 0.638 & 0.980 & 1.007 & -0.069 \\ 
  % 48 & -0.096 & 0.112 & 0.620 & 0.970 & 1.009 & -0.076 \\ 
  % 49 & -0.090 & 0.108 & 0.601 & 0.980 & 1.009 & -0.083 \\ 
  % 50 & -0.087 & 0.119 & 0.662 & 0.990 & 1.009 & -0.029 \\ 
   \hline
\end{tabular}
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
\label{subsetresults}
\end{table}

From the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

@@

Moreover, $\widehat{R}$ could theoretically not be smaller than one, yet it happened several times in this study (see online appendix XYZ). How could $\widehat{R}$ smaller than 1 occur? The number of simulations is smaller than in `regular' MCMC processes[explain why this is positive!]. Therefore, the `$(n-1/n)$' [add equation number] correction factor can influence the estimated potential scale reduction factor. This downwards bias is in the opposite direction than expected: ``The mixture-of-sequences variance, V, should stabilize as a function of n. (Before convergence, we expect $\sigma^2$ to decrease with n, only increasing if the sequences explore a new area of parameter space, which would imply that the original sequences were not overdispersed for the particular scalar summary being monitored.)'' \cite[p~438]{broo98}.

@@

[in discussion, explain that less it is advantage of mi, not a disadv. compared to MCMC. then final par is too negative, explain scope in intro instead.]

>>>>

Why is $\widehat{R}$ not applicable on MI data? $\widehat{R}$ is not appropriate because it assumes over-dispersed initial values, which means that the initial values of the $m$ imputation chains are 'far away' from the distribution that the chains are converging to. With MI procedures, initial values are chosen such that ... [or maybe even estimated from the observed data??]. This means that at most one initial value is necessary, but probably none at all. [I should look this up.]

Starting values of MICE chains: "For each j, fill in starting imputations $Y^0_j$ by random draws from $Y^{obs}_j$." \cite[\S~4.5.2]{buur18} before for loops over variables and imputations, see \url{https://stefvanbuuren.name/fimd/sec-FCS.html#def:mice}

Without over-dispersed initial states, $\widehat{R}$ can falsely diagnose convergence \citep{broo98}. %would not be sensitive enough to flag non-convergence of MI algorithms: "if over-dispersion does not hold, $\sigma_+^2$ can be too low, which can lead to falsely diagnosing convergence." \cite[p~437]{broo98}. 
This suggests that $\widehat{R}$ would not be sensitive enough to flag non-convergence of MI algorithms. Empirical finding, however, show that the opposite may be true: \cite{lace07} report $\widehat{R}$ values above the threshold of $\widehat{R} < 1.1$ after fifty iterations. %that $\widehat{R}$ will not be smaller than 1.1 before iteration number 50. Therefore, the aim is to replicate empirical finding Lacerda et al. 
Hypothesis of this simulation study is that $\widehat{R}$ will over-estimate non-convergence. [Or use:] Hypothesis based on \cite{lace07} is that the conventional acceptable level of $\widehat{R}$ is too strict for MI data. We expect that the simulation diagnostics will indicate valid inference before $\widehat{R}$ will.

@@

\begin{figure}[h]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{Figures/8plotresults.pdf}
  }      
  \caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
    \label{resultssim}
\end{figure}

@@

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 24 19:18:40 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrrr}
  \hline
 & Bias & Emp.SE & CI.width & Cov.rate & R.hat & R.var & Autocorr & AC.var \\ 
  \hline
1 & -0.279 & 0.072 & 0.905 & 0.851 & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} \\ 
  2 & -0.171 & 0.070 & 0.924 & 0.947 & 1.665 & 1.635 & -0.500 & -0.500 \\ 
  3 & -0.162 & 0.068 & 0.901 & 0.954 & 1.322 & 1.306 & -0.660 & -0.660 \\ 
  4 & -0.158 & 0.072 & 0.899 & 0.961 & 1.459 & 1.449 & -0.738 & -0.737 \\ 
  5 & -0.162 & 0.071 & 0.907 & 0.951 & 1.469 & 1.471 & -0.706 & -0.706 \\ 
  6 & -0.160 & 0.072 & 0.910 & 0.962 & 1.252 & 1.256 & -0.652 & -0.658 \\ 
  7 & -0.160 & 0.072 & 0.921 & 0.967 & 1.265 & 1.259 & -0.572 & -0.582 \\ 
  8 & -0.158 & 0.069 & 0.914 & 0.963 & 1.181 & 1.178 & -0.496 & -0.510 \\ 
  9 & -0.162 & 0.072 & 0.923 & 0.963 & 1.188 & 1.182 & -0.434 & -0.472 \\ 
  10 & -0.161 & 0.072 & 0.911 & 0.968 & 1.139 & 1.138 & -0.396 & -0.452 \\ 
  15 & -0.161 & 0.073 & 0.923 & 0.960 & 1.097 & 1.101 & -0.273 & -0.301 \\ 
  20 & -0.158 & 0.070 & 0.916 & 0.971 & 1.067 & 1.066 & -0.187 & -0.212 \\ 
  25 & -0.159 & 0.071 & 0.885 & 0.961 & 1.056 & 1.055 & -0.122 & -0.166 \\ 
  50 & -0.159 & 0.070 & 0.906 & 0.950 & 1.026 & 1.026 & -0.032 & -0.071 \\ 
  100 & -0.157 & 0.069 & 0.921 & 0.973 & 1.013 & 1.013 & 0.012 & -0.013 \\ 
   \hline %{\footnotesize{Note: \textsuperscript{a}  signifies that no convergence diagnostic could be computed.}
\end{tabular}
\end{table}

From \textsuperscript{a} the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

@@

Moreover, $\widehat{R}$ could theoretically not be smaller than one, yet it happened several times in this study (see online appendix XYZ). How could $\widehat{R}$ smaller than 1 occur? The number of simulations is smaller than in `regular' MCMC processes [explain that less iterations is an advantage of MI, not a disadvantage compared to MCMC]. Therefore, the `$(n-1/n)$' [add equation number] correction factor can influence the estimated potential scale reduction factor. This downwards bias is in the opposite direction than expected: ``The mixture-of-sequences variance, V, should stabilize as a function of n. (Before convergence, we expect $\sigma^2$ to decrease with n, only increasing if the sequences explore a new area of parameter space, which would imply that the original sequences were not overdispersed for the particular scalar summary being monitored.)'' \cite[p~438]{broo98}.

@@

[final par is too negative, explain scope in intro instead.]

### 2019-11-24 Simulation/Writeup/NoteConvergence.tex
convergence of chain variances added
updated table and figure

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Nov 12 17:43:11 2019
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrrr}
  \hline
  &\multicolumn{4}{c}{Simulation Diagnostics}& & \multicolumn{2}{c}{Convergence Diagn.} \\
  \cline{2-5} \cline{7-8}
It. & Bias & Emp. SE & CI width & Cov. rate & & $\widehat{R}$ & Auto-corr. \\ 
  \hline
  1 & -0.135 & 0.115 & 0.637 & 0.930 &  & & \\ 
  2 & -0.088 & 0.125 & 0.691 & 0.990 & & 1.499 & -0.500 \\ 
  3 & -0.090 & 0.112 & 0.623 & 0.950 & &  1.200 & -0.658 \\ 
  4 & -0.093 & 0.116 & 0.645 & 0.980 &  & 1.146 & -0.738 \\ 
  5 & -0.087 & 0.108 & 0.599 & 0.980 &  & 1.098 & -0.711 \\ 
  6 & -0.092 & 0.116 & 0.644 & 0.950 & &  1.090 & -0.674 \\ 
  7 & -0.095 & 0.122 & 0.675 & 1.000 & &  1.063 & -0.588 \\ 
  8 & -0.099 & 0.113 & 0.626 & 0.970 & &  1.058 & -0.523 \\ 
  9 & -0.095 & 0.115 & 0.639 & 1.000 & &  1.044 & -0.519 \\ 
  10 & -0.090 & 0.111 & 0.618 & 0.990 & &  1.048 & -0.414 \\ 
  15 & -0.093 & 0.109 & 0.604 & 0.950 & &  1.020 & -0.339 \\ 
  20 & -0.098 & 0.109 & 0.606 & 0.980 & &  1.023 & -0.234 \\ 
  25 & -0.100 & 0.113 & 0.626 & 0.990 &  & 1.016 & -0.091 \\ 
  30 & -0.091 & 0.118 & 0.654 & 0.960 & &  1.014 & -0.153 \\ 
  40 & -0.088 & 0.117 & 0.650 & 0.990 &  & 1.009 & -0.070 \\ 
  50 & -0.087 & 0.119 & 0.662 & 0.990 &  & 1.009 & -0.029 \\ 
  % 11 & -0.100 & 0.127 & 0.704 & 0.970 & 1.046 & -0.360 \\ 
  % 12 & -0.096 & 0.115 & 0.641 & 0.980 & 1.032 & -0.354 \\ 
  % 13 & -0.098 & 0.120 & 0.664 & 0.960 & 1.034 & -0.328 \\ 
  % 14 & -0.094 & 0.113 & 0.630 & 0.990 & 1.030 & -0.353 \\ 
  % 15 & -0.093 & 0.109 & 0.604 & 0.950 & 1.020 & -0.339 \\ 
  % 16 & -0.094 & 0.114 & 0.630 & 0.980 & 1.025 & -0.272 \\ 
  % 17 & -0.091 & 0.116 & 0.645 & 0.980 & 1.028 & -0.243 \\ 
  % 18 & -0.091 & 0.116 & 0.645 & 0.990 & 1.023 & -0.179 \\ 
  % 19 & -0.087 & 0.114 & 0.630 & 0.980 & 1.024 & -0.281 \\ 
  % 20 & -0.098 & 0.109 & 0.606 & 0.980 & 1.023 & -0.234 \\ 
  % 21 & -0.102 & 0.116 & 0.646 & 0.960 & 1.017 & -0.192 \\ 
  % 22 & -0.095 & 0.114 & 0.633 & 0.980 & 1.016 & -0.119 \\ 
  % 23 & -0.088 & 0.107 & 0.595 & 0.980 & 1.017 & -0.246 \\ 
  % 24 & -0.097 & 0.112 & 0.621 & 0.980 & 1.016 & -0.148 \\ 
  % 25 & -0.100 & 0.113 & 0.626 & 0.990 & 1.016 & -0.091 \\ 
  % 26 & -0.096 & 0.113 & 0.628 & 0.980 & 1.017 & -0.177 \\ 
  % 27 & -0.096 & 0.117 & 0.650 & 0.980 & 1.014 & -0.167 \\ 
  % 28 & -0.102 & 0.116 & 0.645 & 0.960 & 1.015 & -0.038 \\ 
  % 29 & -0.098 & 0.114 & 0.632 & 0.990 & 1.016 & -0.137 \\ 
  % 30 & -0.091 & 0.118 & 0.654 & 0.960 & 1.014 & -0.153 \\ 
  % 31 & -0.098 & 0.115 & 0.639 & 0.980 & 1.012 & -0.101 \\ 
  % 32 & -0.096 & 0.113 & 0.626 & 0.940 & 1.011 & -0.095 \\ 
  % 33 & -0.089 & 0.117 & 0.652 & 0.970 & 1.011 & -0.088 \\ 
  % 34 & -0.093 & 0.115 & 0.639 & 0.960 & 1.013 & -0.061 \\ 
  % 35 & -0.103 & 0.115 & 0.638 & 0.970 & 1.011 & -0.126 \\ 
  % 36 & -0.090 & 0.113 & 0.630 & 0.980 & 1.010 & -0.161 \\ 
  % 37 & -0.098 & 0.122 & 0.675 & 0.990 & 1.011 & -0.070 \\ 
  % 38 & -0.095 & 0.118 & 0.656 & 0.970 & 1.011 & -0.119 \\ 
  % 39 & -0.091 & 0.121 & 0.670 & 0.980 & 1.009 & -0.100 \\ 
  % 40 & -0.088 & 0.117 & 0.650 & 0.990 & 1.009 & -0.070 \\ 
  % 41 & -0.095 & 0.117 & 0.648 & 0.960 & 1.010 & -0.148 \\ 
  % 42 & -0.095 & 0.118 & 0.657 & 0.990 & 1.009 & -0.117 \\ 
  % 43 & -0.095 & 0.116 & 0.645 & 0.980 & 1.009 & -0.055 \\ 
  % 44 & -0.101 & 0.125 & 0.692 & 0.980 & 1.009 & -0.068 \\ 
  % 45 & -0.085 & 0.117 & 0.651 & 0.980 & 1.008 & -0.086 \\ 
  % 46 & -0.092 & 0.117 & 0.649 & 0.970 & 1.008 & -0.048 \\ 
  % 47 & -0.095 & 0.115 & 0.638 & 0.980 & 1.007 & -0.069 \\ 
  % 48 & -0.096 & 0.112 & 0.620 & 0.970 & 1.009 & -0.076 \\ 
  % 49 & -0.090 & 0.108 & 0.601 & 0.980 & 1.009 & -0.083 \\ 
  % 50 & -0.087 & 0.119 & 0.662 & 0.990 & 1.009 & -0.029 \\ 
   \hline
\end{tabular}
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
\label{subsetresults}
\end{table}

From the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

>>>>

% % latex table generated in R 3.6.1 by xtable 1.8-4 package
% % Tue Nov 12 17:43:11 2019
% \begin{table}[ht]
% \centering
% \begin{tabular}{lrrrrrrr}
%   \hline
%   &\multicolumn{4}{c}{Simulation Diagnostics}& & \multicolumn{2}{c}{Convergence Diagn.} \\
%   \cline{2-5} \cline{7-8}
% It. & Bias & Emp. SE & CI width & Cov. rate & & $\widehat{R}$ & Auto-corr. \\ 
%   \hline
% ...
% \end{tabular}
% \caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
% \label{subsetresults}
% \end{table}

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 24 19:18:40 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrrr}
  \hline
 & Bias & Emp.SE & CI.width & Cov.rate & R.hat & R.var & Autocorr & AC.var \\ 
  \hline
1 & -0.279 & 0.072 & 0.905 & 0.851 & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} \\ 
  2 & -0.171 & 0.070 & 0.924 & 0.947 & 1.665 & 1.635 & -0.500 & -0.500 \\ 
  3 & -0.162 & 0.068 & 0.901 & 0.954 & 1.322 & 1.306 & -0.660 & -0.660 \\ 
  4 & -0.158 & 0.072 & 0.899 & 0.961 & 1.459 & 1.449 & -0.738 & -0.737 \\ 
  5 & -0.162 & 0.071 & 0.907 & 0.951 & 1.469 & 1.471 & -0.706 & -0.706 \\ 
  6 & -0.160 & 0.072 & 0.910 & 0.962 & 1.252 & 1.256 & -0.652 & -0.658 \\ 
  7 & -0.160 & 0.072 & 0.921 & 0.967 & 1.265 & 1.259 & -0.572 & -0.582 \\ 
  8 & -0.158 & 0.069 & 0.914 & 0.963 & 1.181 & 1.178 & -0.496 & -0.510 \\ 
  9 & -0.162 & 0.072 & 0.923 & 0.963 & 1.188 & 1.182 & -0.434 & -0.472 \\ 
  10 & -0.161 & 0.072 & 0.911 & 0.968 & 1.139 & 1.138 & -0.396 & -0.452 \\ 
  15 & -0.161 & 0.073 & 0.923 & 0.960 & 1.097 & 1.101 & -0.273 & -0.301 \\ 
  20 & -0.158 & 0.070 & 0.916 & 0.971 & 1.067 & 1.066 & -0.187 & -0.212 \\ 
  25 & -0.159 & 0.071 & 0.885 & 0.961 & 1.056 & 1.055 & -0.122 & -0.166 \\ 
  50 & -0.159 & 0.070 & 0.906 & 0.950 & 1.026 & 1.026 & -0.032 & -0.071 \\ 
  100 & -0.157 & 0.069 & 0.921 & 0.973 & 1.013 & 1.013 & 0.012 & -0.013 \\ 
   \hline %{\footnotesize{Note: \textsuperscript{a}  signifies that no convergence diagnostic could be computed.}
\end{tabular}
\end{table}

From \textsuperscript{a} the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].
